Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-10 podc16/paper2.tex
map-agreement section

\section{Leaderless Algorithms}

@@

A dependency-set algorithm exposes the input interface $\texttt{announce}_p\left( c \right)$, where $c$ is a command, and the output interface $\texttt{suggest}_p \left( c,\mathcal{D}\right)$, where $p\in P$ is the process executing the call.  
Moreover, a dependency-set algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion $\texttt{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before.
    \item For any two suggestions $\texttt{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\texttt{suggest}_q \left( c_2,\mathcal{D}_2\right)$ (with $p$ possibly equal to $q$),  if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
\end{enumerate}

@@

A map-agreement algorithm exposes the input actions ${propose\left( c, d \right)}^p$ and the output actions ${decide\left( c, d \right)}^p$, for a command $c$, a set of commands $d$, and a process $p$.
Moreover, a map-agreement algorithm must ensure that: 
\begin{enumerate}[noitemsep,nolistsep]
    \item If the set of dependencies $d$ is decided for a command $c$, then $d$ has been proposed for $c$ at an earlier time.
    \item If $d_1$ is decided for a command $c$ and $d_2$ is decided for the same command $c$, then $d_1$ is equal to $d_2$.
\end{enumerate}
Note that any SMR algorithm, like MultiPaxos, can be used to implementing map-agreement by uniquely associating commands to MultiPaxos instance numbers.

>>>>

\section{Leaderless Generalized Consensus Algorithms}

@@

A dependency-set algorithm exposes the input interface $\texttt{announce}_p\left( c \right)$, to announce a command $c$, and the output interface $\texttt{suggest}_p \left( c,\mathcal{D}\right)$, to suggest a set of dependencies $\mathcal{D}$ for $c$, where $p\in P$ is the process executing the call.  
Moreover, a dependency-set algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion $\texttt{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before.
    \item For any two suggestions $\texttt{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\texttt{suggest}_q \left( c_2,\mathcal{D}_2\right)$ (with $p$ possibly equal to $q$),  if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
\end{enumerate}

@@

A map-agreement algorithm exposes the input interface $\texttt{propose}_p\left( c, \mathcal{D} \right)$, to propose a set of dependencies $\mathcal{D}$ for a command $c$, and the output interface $\texttt{decide}_p\left( c, \mathcal{D} \right)$, to decide $\mathcal{D}$ for $c$, where $p\in P$ is the process executing the call.
Moreover, a map-agreement algorithm must ensure that: 
\begin{enumerate}[noitemsep,nolistsep]
    \item If the set of dependencies $\mathcal{D}$ is decided for a command $c$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time.
    \item If $\mathcal{D}_1$ is decided for a command $c$ and $\mathcal{D}_2$ is decided for the same command $c$, then $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.
 \end{enumerate}

\todo{OR MORE FORMALLY}

\begin{enumerate}[noitemsep,nolistsep]
    \item For any decision $\texttt{decide}_p\left( c, \mathcal{D} \right)$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time.
    \item For any two decisions $\texttt{decide}_p\left( c, \mathcal{D}_1 \right)$, $\texttt{decide}_q\left( c, \mathcal{D}_2 \right)$ (with $p$ possibly equal to $q$), then $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.

\end{enumerate}

Note that any SMR algorithm, like MultiPaxos, can be used to implementing map-agreement by uniquely associating commands to MultiPaxos instance numbers.
